International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-21 paper/4_app.tex
still deets to finish tomorrow

\begin{figure}
\centering   
	\subfigure[AUC]{\label{fig:weeksauc}\includegraphics[width=65mm]{weeks_auc_outsamp.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{weeks_pr_outsamp.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves}
\end{figure}

@@

\begin{figure}
	\caption{}
	\includegraphics[width=\textwidth]{gibler_srmvc.pdf}
 	\label{fig:gibmargeff}
 \end{figure}

>>>>

\begin{figure}
\centering   
	\subfigure[AUC]{\label{fig:weeksauc}\includegraphics[width=.45\textwidth]{weeks_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{weeks_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves}
\end{figure}

@@

\begin{figure}
	\caption{}
	\includegraphics[width=\textwidth]{gibler_margeff.pdf}
 	\label{fig:gibmargeff}
 \end{figure}
